Discussion

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
discussion on Corrugator as predictor of SVs

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020]. <!-- evtl. Einwand warum Suppression am erfolgreichsten war --> 
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
Both measures also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
We believe that there was a good basis on which individual SVs of ER strategies could be determined.
Overall, there was evidence to support hypotheses H1 to H5.
It was nevertheless surprising that the strategy suppression showed on average the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
This also indicates why the required effort is the lowest. 
The direct instruction to implement the strategy reduces the complexity of the generation process.
By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort. 
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.

@@

<!-- Argumentation Corrugator nicht zw. Lvl unterschiedlich, aber trotzdem einfluss, weil man da eine relativ direkte Rückmeldung hat + Levator eher nicht -> alle Bilder negativ aber nur einige eklig, wenn man also nur diese Bilder reinnimmt, wird vielleicht Levator signifikant; 
Effort Ergebnisse bestätigen ESER Paper, dass man nach Effort-Minimierung strebt;
Utility: Subjektive Einschätzung der Strategie als Mittel zur Zielerreichung, was eine überschneidung mit dem SV darstellt und außerdem evtl. eine Interaktion von Effektivität und Effort -->

>>>>

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020]. <!-- evtl. Einwand warum Suppression am erfolgreichsten war --> 
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
Both measures also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
We believe that there was a good basis on which individual SVs of ER strategies could be determined.
Overall, there was evidence to support hypotheses H1 to H5.
It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
This also indicates why the required effort is the lowest. 
The direct instruction to implement the strategy reduces the complexity of the generation process.
By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort. 
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.

@@

As a predictor of ER effectiveness, *corrugator* activity showed a significant association with SVs, but not *levator* activity or subjective arousal.
With regard to the EMG measures, this could be because all the pictures we used were negative, i.e. elicited *corrugator* activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific *levator* activity. 
However, *corrugator* activity did not differ significantly between ER strategies, but was still associated with SVs. 
One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current stragey, much more direct than, for example, the subjective arousal rating at the end of each experimental block.

<!--  
Effort Ergebnisse bestätigen ESER Paper, dass man nach Effort-Minimierung strebt;
Utility: Subjektive Einschätzung der Strategie als Mittel zur Zielerreichung, was eine überschneidung mit dem SV darstellt und außerdem evtl. eine Interaktion von Effektivität und Effort -->
